Helixer: Cross-species Gene Annotation Of Large Eukaryotic Genomes Using Deep Learning

### 2020-07-31 paper/main.tex
minor, institute

\title[short Title]{Helixer: Cross-species Gene Annotation Of Large Eukaryotic Genomes Using Deep Learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1}}$, Marvin Steinborn\,$^{\text{\sfb 1}}$, Stephan Scholz, Daniela Dey\,$^{\text{\sfb 2}}$, Andreas P.M. Weber\,$^{\text{\sfb 1}}$, Alisandra K. Denton\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany\\
$^{\text{\sf 2}}$Institute of Human Genetics, Medical Faculty, RWTH Aachen University, Aachen, 52062, Germany}

>>>>

\title[short Title]{Helixer: Cross-species Gene Annotation Of Large Eukaryotic Genomes Using Deep Learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1}}$, Marvin Steinborn\,$^{\text{\sfb 1}}$, Stephan Scholz, Daniela Dey\,$^{\text{\sfb 2}}$, Andreas P.M. Weber\,$^{\text{\sfb 1}}$, Alisandra K. Denton\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue of Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, 40225, Germany\\
$^{\text{\sf 2}}$Institute of Human Genetics, Medical Faculty, RWTH Aachen University, Aachen, 52062, Germany}
